---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dockerstats

<!-- badges: start -->
<!-- badges: end -->

`{dockerstats}` is a small wrapper around `docker stats` that returns the output of this command as an R data.frame. 

Note that this package calls `system("docker stats")` so you should be able to do this from your R command line. I'll probably refactor that at some point. 

## Installation

You can install the released version of `{dockerstats}` from GitHubwith:

``` r
remotes:install_github("ColinFay/dockerstats")
```

## How to 

```{r}
library(dockerstats)
```


### dockerstats()

By default, `dockerstats()` returns the stats for running containers. 

```{r}
dockerstats()
```

You can return stats for all containers (not just running)

```{r}
dockerstats(all = TRUE)
```

Or from a subset of containers:

```{r}
dockerstats("mongo", "proxy")
```

The `extra` param is used to add extra information to the recording, which can be usefull is you want to tag the specific recording. 

For example, here we mimic a connection on the `hexmake` container

```{r echo = FALSE}
system("docker run --name hexmake --rm -p 2811:80 colinfay/hexmake", wait = FALSE)
Sys.sleep(5)
```

```{r eval = FALSE}
system("docker run --name hexmake --rm -p 2811:80 colinfay/hexmake", wait = FALSE)

```



```{r, eval = FALSE}
library(crrri)
chrome <- Chrome$new(
  bin = pagedown::find_chrome(), 
  debug_port = httpuv::randomPort()
)

client <- chrome$connect(callback = function(client) {
  client
})

Page <- client$Page
Page$navigate(url = "http://localhost:2811")

dockerstats::dockerstats("hexmake", extra = "Connection via chrome")

chrome$close()
```


### dockerstats_recurse

`dockerstats_recurse()` is a wrapper around `dockerstats()` that runs every `every` seconds, calling the `callback` function everytime a loop is completed. 

By default, the callback is `print`, but you can define your own. For example, this function will run the `dockerstats()` fun every 2 seconds and save it to a file. 

```{r eval = FALSE}
dockerstats_recurse(
  "hexmake",
  callback = function(res){
    print(
      paste("Mem usage: ", res$MemUsage)
    )
    write.table(
      res, 
      "dockerstats.csv", 
      append = TRUE, 
      col.names = FALSE, 
      row.names = FALSE, 
      sep = ","
    )
  }
)
```

As this is a pretty common use-case, a wrapper for this is implemented: 

```{r eval = FALSE}
dockerstats_recurse(
  "hexmake",
  callback = append_csv("dockerstats.csv", print = TRUE)
)
```


## How columns are transformed

+ `CPUPerc` and `MemPerc` are stripped from the trailing `%`, and are turned into numeric

+ `MEM USAGE / LIMIT` is splitted into two columns, `MemUsage` and `MemLimit

+ `NET I/O` and `BLOCK I/O` are splitted into two columns, respectively `NetI` & `NetO`, and `BlockI` & `BlockO`

## Manupulate columns expressed in bite size

You can call `as_fs_byte()` from the `{fs}` package to manipulate the columns which are expressed in bytes. 

Note that you'll need to install the `{fs}` package (it's not imported by `{dockerstats}`).

```{r}
dock_stats <- dockerstats()
dock_stats$MemUsage <- fs::as_fs_bytes(
  dock_stats$MemUsage
)
```

```{r}
dock_stats[ which.max(dock_stats$MemUsage) , ]
```

```{r}
dock_stats[ which.min(dock_stats$MemUsage) , ]
```

```{r}
library(ggplot2)
ggplot(
  dock_stats, 
  aes(
    reorder(Name, MemUsage), 
    MemUsage)
) + 
  geom_col() +
  scale_y_continuous(labels = scales::comma) + 
  coord_flip() + 
  labs(
    title = "MemUsage of running containers", 
    y = "MemUsage in bytes"
  )
```

```{r}
system("docker kill hexmake")
```
